Latitudinal gradients in biotic niche breadth vary across ecosystem types.

### 2018-07-26 manuscript/latitudepaper.tex
removed a couple of old strikethroughs in the main text

  Unlike other ecosystem types, the scaling of generality in lake and stream
  food webs was stronger (i.e., generality increased more steeply with
  increasing species richness) in higher-latitude food webs. \st{In lake food webs,
  this trend was echoed in the scaling relationships between species richness
  and vulnerability and links per species.} This means that species in tropical
  freshwater communities gain fewer additional feeding links per additional
  species in the web\st{ and that species in tropical lakes also gain fewer
  predators, and fewer links in general, per additional species than species
  in high-latitude lakes}. These trends are consistent with the hypothesis that
  greater stability in the tropics leads to narrower niches~\cite{Vazquez2004}
  and a higher proportion of specialists.

@@

  Importantly, while terrestrial communities are also strongly seasonal at
  high latitudes and can receive significant allochthonous
  inputs~\cite{Nakano2001}, terrestrial consumers tend to be
  morphologically specialised for feeding on particular prey~\cite{Liem1990}.
  This means that primarily gape-limited aquatic consumers tend to be more
  generalist across all types of aquatic habitats than terrestrial 
  consumers~\cite{Liem1990,Shurin2006}. This trend also held in our data, although the difference between generality was not significant (
  $\mu_{Aquatic}$=\st{5.47}5.71, $\mu_{Terrestrial}$=\st{3.82}4.82; $p$=\st{0.007}0.297 for $\mu_{Aquatic}$\textgreater$\mu_{Terrestrial}$). 
  The key to this argument is therefore whether freshwater ecosystems experience
  more severe seasonal variation than marine and estuarine ecosystems. Although
  we are not aware of any study explicitly comparing seasonal variation in
  fresh and saltwater ecosystems at similar latitudes, we believe that freshwater 
  ecosystems are indeed likely to experience more severe changes because of their small size.
  While oceans and estuaries certainly vary in terms of water temperature and
  nutrients over the course of a year~\cite{Baird1989}, these changes are likely to be slower
  and milder than in freshwaters because marine and estuarine communities are buffered 
  by being open to the ocean rather than isolated in the midst of a terrestrial matrix. 
  Supporting this hypothesis, net primary productivity is much more variable over the course of a year 
  in non-marine communities~\cite{Field1998}. Thus suggests that niche breadths may also be 
  more variable over the course of the year.

>>>>

  Unlike other ecosystem types, the scaling of generality in lake and stream
  food webs was stronger (i.e., generality increased more steeply with
  increasing species richness) in higher-latitude food webs. In lake food webs,
  this trend was echoed in the scaling relationships between species richness
  and vulnerability and links per species. This means that species in tropical
  freshwater communities gain fewer additional feeding links per additional
  species in the web and that species in tropical lakes also gain fewer
  predators, and fewer links in general, per additional species than species
  in high-latitude lakes. These trends are consistent with the hypothesis that
  greater stability in the tropics leads to narrower niches~\cite{Vazquez2004}
  and a higher proportion of specialists.

@@

  Importantly, while terrestrial communities are also strongly seasonal at
  high latitudes and can receive significant allochthonous
  inputs~\cite{Nakano2001}, terrestrial consumers tend to be
  morphologically specialised for feeding on particular prey~\cite{Liem1990}.
  This means that primarily gape-limited aquatic consumers tend to be more
  generalist across all types of aquatic habitats than terrestrial 
  consumers~\cite{Liem1990,Shurin2006}. This trend also held in our data, although the difference between generality was not significant (
  $\mu_{Aquatic}$=\st{5.47}5.86, $\mu_{Terrestrial}$=\st{3.82}3.75; $p$=\st{0.007}\textless0.001 for $\mu_{Aquatic}$\textgreater$\mu_{Terrestrial}$). 
  The key to this argument is therefore whether freshwater ecosystems experience
  more severe seasonal variation than marine and estuarine ecosystems. Although
  we are not aware of any study explicitly comparing seasonal variation in
  fresh and saltwater ecosystems at similar latitudes, we believe that freshwater 
  ecosystems are indeed likely to experience more severe changes because of their small size.
  While oceans and estuaries certainly vary in terms of water temperature and
  nutrients over the course of a year~\cite{Baird1989}, these changes are likely to be slower
  and milder than in freshwaters because marine and estuarine communities are buffered 
  by being open to the ocean rather than isolated in the midst of a terrestrial matrix. 
  Supporting this hypothesis, net primary productivity is much more variable over the course of a year 
  in non-marine communities~\cite{Field1998}. Thus suggests that niche breadths may also be 
  more variable over the course of the year.
